### 2013-02-14 MSteenhagen-CV.tex
Added Ockham Society talk
Added editorship PJA and membership P&PGroup

\ind Dissertation research on the nature of human experience of pictorial representations. Supervisor: Prof. Mark Eli Kalderon.

@@

@@

@@

\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Talks}
\medskip

>>>>

\ind Dissertation research on the nature of human experience of pictorial representation. Supervisor: Prof. Mark Eli Kalderon.

@@

\ind Editor, \href{http://www.pjaesthetics.org}{\emph{Postgraduate Journal of Aesthetics}}

\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy \& Psychoanalysis Group}

\bigskip
\bigskip

@@

\bigskip
\bigskip

@@

\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Talks}
\medskip
\ind 2013. ``Pictures \& perceptual knowledge'' The Ockham Society, Department of Philosophy, University of Oxford.
